\LARGE \bf Longitudinal Trajectory Planning and Tracking for Fixed-Path Autonomous Driving

### 2016-01-19 paper1.tex
updated indiviual jerk profile sections

For each of the profiles, it is possible that the chosen values of $\mathbf{a}_m$ and $\mathbf{j}_m$ will not be feasible for a desired speed at the end of the phase.
This results in a negative time interval for that phase.
In many cases, modifying $\mathbf{a}_m$ and $\mathbf{j}_m$ such that they still lie within $\mathbf{a}^{max}_m$ and $\mathbf{j}^{max}_m$ will remedy this.
Specifically, jerk may be increased while peak acceleration is decreased.
If no acceptable values are found within the valid ranges of $\mathbf{a}^{max}_m$ and $\mathbf{j}^{max}_m$, a new jerk profile must be chosen.

@@

This profile, described above, is always attempted first.
All time steps have a single solution, enabled by the fact that the initial and end conditions are known, and the two peak accelerations and two jerk magnitudes are provided as configuration parameters.

@@

In the case mentioned above, the speed limit is too high for a solution to exist for a 7 phase profile.
The middle travel period is removed, so that the vehicle increases speed and then immediately decreases speed. 
The peak speed in this case has a solution, but cannot be manipulated directly.

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.7\columnwidth]{graphics/4phase_v(s).png}
  \caption{4 phase profile, displayed as speed vs. position along path.}
  \label{fig:4phaseprofile}
\end{figure}

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.7\columnwidth]{graphics/4Rphase_all_derivatives.png}
  \caption{Reversed 4 phase profile, displayed as speed vs. position along path.}
  \label{fig:4rphaseprofile}
\end{figure}

@@

A change from one speed to another.
All of the above profiles are composed of some combination of a 3 phase profile and a $j_k = 0$ phase.
This presents a difficulty in that either $L$ or $v_f$ may be enforced, but not both (there is no solution to enforce both).
As such, this profile is chosen for a segment in which it is impossible to completely arrive at the end speed given the initial speed.

>>>>

For each of the profiles, it is possible that the chosen values of $\mathbf{a}_m$ and $\mathbf{j}_m$ will not be feasible for a desired speed at the end of the phase.
This results in a negative time interval for that phase.
In many cases, modifying $\mathbf{a}_m$ and $\mathbf{j}_m$ such that they still lie within $\mathbf{a}^{max}_m$ and $\mathbf{j}^{max}_m$ will remedy this.
Specifically, jerk may be increased while peak acceleration is decreased.
This process is referred to herein as ``accel-jerk tuning''
If no acceptable values are found within the valid ranges of $\mathbf{a}^{max}_m$ and $\mathbf{j}^{max}_m$, a new jerk profile must be chosen.

@@

This profile, described above, is always attempted first.
All time steps have a single solution, enabled by the fact that the initial and end conditions are known, and the two peak accelerations and two jerk magnitudes are provided as configuration parameters.
In the case where $\Delta t_2$ or $\Delta t_6$ are negative, accel-jerk tuning must be employed.
In the instance where $\Delta t_4$ is negative, the total segment length $L$ is too short to reach top speed of $v_m$, so a 6 phase profile must be used.

@@

In the case mentioned above, the speed limit is too high for a solution to exist for a 7 phase profile.
The middle travel period $\Delta t_4$ is removed, so that the vehicle increases speed and then immediately decreases speed. 
The peak speed in this case has a solution, but cannot be manipulated directly.
Without this known value, the problem becomes underdefined, so $\Delta t_2$ and $\Delta t_5$ each have two solutions: one negative and one positive.
The positive solution is chosen.
In the case where both solutions are negative, accel-jerk tuning is attempted. 
Should that yield no positive time intervals, one of the two 4 phase profiles then becomes appropriate, since $L$ is not large enough to accomodate accelerating past the end speed.
If $v_i > v_f$, then a reversed 4 phase profile is attempted.
However, if $v_i > v_f$, then a regular 4 phase profile is attempted.

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.7\columnwidth]{graphics/4phase_v(s).png}
  \caption{4 phase profile, displayed as speed vs. position along path within the segment.}
  \label{fig:4phaseprofile}
\end{figure}

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.7\columnwidth]{graphics/4Rphase_all_derivatives.png}
  \caption{Reversed 4 phase profile, displayed as speed vs. position along path within the segment.}
  \label{fig:4rphaseprofile}
\end{figure}

@@

A change from one speed to another.
All of the above profiles are composed of some combination of a 3 phase profile and a $j_k = 0$ phase.
This presents a difficulty in that either $L$ or $v_f$ may be enforced, but not both (there is no solution to enforce both).
As such, this profile is chosen only for a segment in which it is impossible to completely arrive at the end speed given the initial speed, so fitting one of the two 4 phase profiles has been attempted and subsequently failed.
